\textit{Supplementary Material} \\ Predicting Solid State Material Platforms for Quantum Technologies

### 2022-03-11 supplementary.tex
Updates from Overleaf

The relevant hyperparameters for logistic regression were the regularization strength and the maximum iterations, which were set to $0.46$ and $400$, respectively. Smaller regularization values resulted in worse scores, while increasing values did not noticeably affect the results. The decision trees and random forests methods both found an optimal maximum depth of seven, where smaller values resulted in low precision but high recall.  Therefore, the choice was made to facilitate a compromise between precision and recall. For gradient boosting, we find the optimal maximum depth as four due to a decline in overall metrics for increasing depth except for training accuracy. An increasing depth  could potentially result in overfitting.

@@

Lastly, we turn to the empirical approach to data labeling, which resulted in $404$ unsuitable and $202$ suitable candidates through the initial selection process. However, in contrast to the two labeled datasets discussed above, the majority of the entries was in this case labeled as unsuitable candidates.

@@

The optimal hyperparameters are summarized in Table~\ref{tab:03-pca}, where all ML methods exhibit high evaluation metrics. Importantly, we find the difference in the number of principal components as most prominent, where logistic regression finds an optimum at $61$ with the F$1$-score of $0.98$. Decision trees uses only $9$ principal components to achieve an F$1$ score of $0.95$, while random forests needs $27$ principal components to gain an F$1$ score of $0.97$.

@@

Lastly, gradient boosting performs optimally at $13$ principal components with a mean F$1$-score of $0.96$. The relevant hyperparameters were the regularization term for logistic regression, which was set to $0.021$, and the maximum number of iterations at $400$. The decision trees uses a maximum depth of $6$, where larger values increased the training accuracy but not any other metric. The maximum depth for  random forests was set to $6$. For gradient boosting, which uses a weak learner, the depth of the trees was set to  $4$.

>>>>

The relevant hyperparameters for logistic regression were the regularization strength and the maximum iterations, which were set to $0.46$ and $400$, respectively. Smaller regularization values resulted in worse scores, while increasing values did not noticeably affect the results. The decision trees and random forests methods both found an optimal maximum depth of seven, where smaller values resulted in low precision but high recall.  Therefore, the choice was made to facilitate a compromise between precision and recall. For gradient boosting, we find the optimal maximum depth to be four due to a decline in overall metrics for increasing depth.
That is, except for the training accuracy, demonstrating a case of potential overfitting.

@@

Lastly, we turn to the data labeling using the empirical approach, which resulted in $404$ unsuitable and $202$ suitable candidates through the initial selection process. However, in contrast to the two labeled datasets discussed above, the majority of the entries was in this case labeled as unsuitable candidates.

@@

The optimal hyperparameters are summarized in Table~\ref{tab:03-pca}, where all ML methods exhibit high evaluation metrics. Importantly, we find the difference in the number of principal components as most prominent, where logistic regression finds an optimum at $61$ with an F$1$-score of $0.98$. Decision trees uses only $9$ principal components to achieve an F$1$ score of $0.95$, while random forests needs $27$ principal components to gain an F$1$ score of $0.97$.

@@

Lastly, gradient boosting performs optimally at $13$ principal components with a mean F$1$-score of $0.96$. The relevant hyperparameters were the regularization term for logistic regression, which was set to $0.021$, and the maximum number of iterations at $400$. The decision trees uses a maximum depth of $6$, where larger values only increased the training accuracy. The maximum depth for  random forests was set to $6$. For gradient boosting, which uses a weak learner, the depth of the trees was set to  $4$.
